---
title: "MOVIE"
author: "ANWAR ABU ALHUSSEIN"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE, include=TRUE)
```
 
## Required packages
###########################################################################
###########################################################################
###                                                                     ###
###                    HEART FAILURE CLINICAL                           ###
###                   PROJECT LINEAR REGRESSION                         ###
###                                                                     ###
###########################################################################
###########################################################################
###*                        Loading Packages
###*                        ----------------
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(caret))
suppressPackageStartupMessages(library(ggcorrplot))
suppressPackageStartupMessages(library(Metrics))
suppressPackageStartupMessages(library(corrplot))
suppressPackageStartupMessages(library(bannerCommenter))
suppressPackageStartupMessages(library(psych))
suppressPackageStartupMessages(library(WVPlots))
suppressPackageStartupMessages(library(PerformanceAnalytics))
suppressPackageStartupMessages(library(car))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(outliers))
suppressPackageStartupMessages(library(broom))
suppressPackageStartupMessages(library(equatiomatic))
```




##===============================================================
##                     Reading in the data                     ==
##===============================================================
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
download.file("https://raw.githubusercontent.com/ABUALHUSSEIN/test/main/data/movie.csv",
              destfile = "movie.csv")
```

##source(destfile)
##ls()
#======================================
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
setwd("C:/Users/WAFA/Desktop")
movie <- read.csv("movie.csv",header=TRUE)
View(movie)
```

## Missing Data. We are looking for the missing values
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
is.na(movie)
sum(is.na(movie))
```

# Check the column names again, 
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
colnames(movie)
```

# The names contain dots, I will substitute 
# each dot with underscore "_"
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
var_names <- gsub("\\.", "_", colnames(movie))
var_names[14] <- "Aggregate_Followers"
var_names[14]
colnames(movie) <- var_names
colnames(movie)
View(movie)
```



#  Gives the name of columns that do not have data ------------------------
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
list_na <- colnames(movie)[ apply(movie, 2, anyNA) ]
list_na
```
##===============================================================
## Now we need to compute of the mean with the argument na.rm = TRUE. 
#This argument is compulsory because the columns have missing data, 
# and this tells R to ignore them.              
##===============================================================

# Create mean -------------------------------------------------------------

```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
average_missing <- apply(movie[,colnames(movie) %in% list_na],
                         2,
                         mean,
                         na.rm =  TRUE)
average_missing

```

# Replace the NA Values ---------------------------------------------------
##===============================================================
##The verb mutate from the dplyr library is useful in creating a new variable.
#We don't necessarily want to change the original column so we can create a new variable without the NA.
#mutate is easy to use, 
# we just choose a variable name and define how to create this variable        
##===============================================================
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
movie_replace <- movie %>%
  mutate(replace_mean_Year  = ifelse(is.na(Year), average_missing[1], Year),
         replace_mean_Sequel = ifelse(is.na(Sequel), average_missing[2], Sequel),
         replace_mean_Sentiment = ifelse(is.na(Sentiment), average_missing[3], Sentiment),
         replace_mean_Genre = ifelse(is.na(Genre), average_missing[4], Genre),
         replace_mean_Ratings  = ifelse(is.na(Ratings), average_missing[5],Ratings),
         replace_mean_Gross  = ifelse(is.na(Gross), average_missing[6], Gross),
         replace_mean_Budget  = ifelse(is.na(Budget), average_missing[7], Budget),
         replace_mean_Screens  = ifelse(is.na(Screens), average_missing[8], Screens),
         replace_mean_Views  = ifelse(is.na(Views), average_missing[9], Views),
         replace_mean_Likes  = ifelse(is.na(Likes), average_missing[10],Likes),
         replace_mean_Dislikes = ifelse(is.na(Dislikes), average_missing[11],Dislikes),
         replace_mean_Comments = ifelse(is.na(Comments), average_missing[12], Comments),
         replace_mean_Aggregate_Followers  = ifelse(is.na(Aggregate_Followers), 
                                              average_missing[13], Aggregate_Followers))
```

#  Perform the replacement ------------------------------------------------

```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
sum(is.na(movie_replace$Year))
sum(is.na(movie_replace$Sequel))
sum(is.na(movie_replace$Sentiment))
sum(is.na(movie_replace$Genre))
sum(is.na(movie_replace$Ratings))
sum(is.na(movie_replace$Gross))
sum(is.na(movie_replace$ Budget))
sum(is.na(movie_replace$ Screens))
sum(is.na(movie_replace$ Views))
sum(is.na(movie_replace$Likes))
sum(is.na(movie_replace$Dislikes))
sum(is.na(movie_replace$Comments))
sum(is.na(movie_replace$Aggregate_Followers))

```

```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
sum(is.na(movie_replace$replace_mean_Aggregate_Followers))
```
## My new Data.
# Here I created a new frame for the data that  do not  contain  na values 
# Select all columns that  do not  contain  na values from a data  by names --------
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
new_movie<- movie_replace %>%
  select(replace_mean_Year, replace_mean_Sequel,replace_mean_Sentiment,replace_mean_Genre,replace_mean_Ratings,
      replace_mean_Gross,replace_mean_Budget,replace_mean_Screens,replace_mean_Views,
   replace_mean_Likes,replace_mean_Dislikes,replace_mean_Comments,replace_mean_Aggregate_Followers)
view(new_movie) 
sum(is.na(new_movie))
```

# Select all columns that  do not  contain  na values from a data by index --------
```{r}
new_movie<- movie_replace  %>% select(15:27)
sum(is.na(new_movie))
```

#  Other Ways of replace the NA Values ------------------------------------

```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}

new_movie<- data.frame(
  sapply(
    movie,
    function(x) ifelse(is.na(x),
                       mean(x, na.rm = TRUE),
                       x)))
new_movie
sum(is.na(new_movie))
```


#txt <- "Explore the data set"
#banner(txt, centre = TRUE, bandChar = "-")
##----------------------------------------------------------------
##                     Explore the data set                     --
##----------------------------------------------------------------

#txt <- "Data contents"
#banner(txt, centre = TRUE, bandChar = "=")
##===============================================================
##                        Data contents                        ==
##===============================================================
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
Hmisc::contents(new_movie)
psych::describe(new_movie, skew = TRUE, 
                IQR = TRUE)
glimpse(new_movie)

head(new_movie, 10)

tail(new_movie)

car::brief(new_movie)
str(new_movie)
```


# We have 232 obs. of  14 variables

##================================================================
##                EDA: Exploratory Data Analysis                ==
##================================================================
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
movie_data <- new_movie[,6:ncol(new_movie)]
```


# Check the column names again, 
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
colnames(movie_data)
```
#txt <- "Get the summary statistics of the variables"
#banner(txt, centre = TRUE, bandChar = "*")
##***************************************************************
##         Get the summary statistics of the variables         **
##***************************************************************

```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
summary(movie_data)
Hmisc::describe(movie_data)
psych::describe(movie_data, skew = TRUE, 
                IQR = TRUE)
```




#txt <- "The Dependent Variables in this study is  Ratings"
#banner(txt, centre = TRUE, bandChar = ":")

##::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
##  The Dependent Variables in this study is  Ratings "replace_mean_Ratings" ::
##::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# We are going to explore the distribution of this variable
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
movie_replace
View(movie_replace)
movie_data <- movie_replace[,19:ncol(movie_replace)]
View(movie_data)
colnames(movie_data)
ggplot(movie_data, aes(x = replace_mean_Ratings)) + 
  geom_histogram(aes(y = ..density..), 
                 fill = "steelblue") +
  geom_density(color = "red", lwd = 1.2) + 
  stat_function(fun = dnorm, args = list(mean = mean(movie_data$replace_mean_Ratings), 
                                         sd = sd(movie_data$replace_mean_Ratings)),
                color = "orange", lwd = 1.2) +
  theme_linedraw()

```


#################################################################
##                        Joint Graphs                         ##
#################################################################

```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
library(WVPlots)
```

#replace_mean_Ratings VS  replace_mean_Budget
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
ScatterHist(movie_data, title = "replace_mean_Ratings VS  replace_mean_Budget", 
            xvar = "replace_mean_Budget", yvar = "replace_mean_Ratings", 
            smoothmethod = "lm")
```
## There is  a positive  linear relationshipbetween the variables(replace_mean_Ratings & replace_mean_Budget)
#replace_mean_Ratings VS  replace_mean_Gross
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
ScatterHist(movie_data, title = "replace_mean_Ratings VS  replace_mean_Gross", 
            xvar = "replace_mean_Gross", yvar = "replace_mean_Ratings", 
            smoothmethod = "lm")
```
## There is  a positive  linear relationshipbetween the variables(replace_mean_Ratings & replace_mean_Gross)

# replace_mean_Ratings VS replace_mean_Views 
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
ScatterHist(movie_data, title = "replace_mean_Ratings VS  replace_mean_Views", 
            xvar = "replace_mean_Views", yvar = "replace_mean_Ratings", 
            smoothmethod = "lm")
```


# There is a very weak relationship between the variables(replace_mean_Ratings & replace_mean_Views )

# replace_mean_Ratings VS replace_mean_Dislikes 
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
ScatterHist(movie_data, title = "replace_mean_Ratings VS  replace_mean_Dislikes", 
            xvar = "replace_mean_Dislikes", yvar = "replace_mean_Ratings", 
            smoothmethod = "lm")
```


# There is a negative linear relationship between the variables(replace_mean_Ratings & replace_mean_Dislikes )


# replace_mean_Ratings VS replace_mean_Likes
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
ScatterHist(movie_data, title = "replace_mean_Ratings VS  replace_mean_Likes", 
            xvar = "replace_mean_Likes", yvar = "replace_mean_Ratings", 
            smoothmethod = "lm", hist_color = "#00ACBB", 
            point_alpha = 0.3, 
            point_color = "#FF00CC")
```

# There is  a positive linear relationship between the variables (replace_mean_Ratings & replace_mean_Likes)

# replace_mean_Dislikes VS replace_mean_Likes
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
ScatterHist(movie_data, title = "replace_mean_Dislikes VS  replace_mean_Likes", 
            xvar = "replace_mean_Likes", yvar = "replace_mean_Dislikes", 
            smoothmethod = "lm", hist_color = "#00ACBB", 
            point_alpha = 0.3, 
            point_color = "#FF00CC")
```

# There is  a positive linear relationship between the variables (replace_mean_Dislikes & replace_mean_Likes)

##***************************************************************
##                    Study the correlation                    **
##***************************************************************
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
psych::lowerCor(x = movie_data)
psych::corr.test(movie_data)$p
```


# Plotting the ScatterPlotMatrix
# First look at the help, and the arguments 
# I am going to tweak the knobs a little
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
pairs(movie_data)  
```

#change the color and get halp matrix
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
pairs(movie_data, lower.panel = NULL, col= "blue")
```

# Or if you want only the lower part matrix
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
pairs(movie_data, upper.panel = NULL, col= "blue")
```

# Check the documentation for more information
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
?pairs
```

# Scatter Matrix with psych package
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
library(psych)
pairs.panels(movie_data, 
             method = "pearson", # Correlation method
             hist.col = "#11AACC",
             density = TRUE, 
             cex.cor = 1.3, 
             col = "red", 
             lm = TRUE, 
             pch = 25,    # point character
             bg = "cyan") # background
```

# Scatter Matrix with car package
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
car::scatterplotMatrix(movie_data, 
                       col = "steelblue", 
                       pch = 21, 
                       upper.panel = NULL)
```


# Lastly
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}

library(PerformanceAnalytics)
chart.Correlation(movie_data, 
                  histogram=TRUE,
                  pch=19, 
                  col = "blue")

```


##***************************************************************
##                  correlation plot matrices                  **
##***************************************************************
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
correl <- cor(movie_data)

psych::cor.plot(correl)

corrplot::corrplot(correl)
```

# Tweak the knobs
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}

corrplot(correl, type = "upper", 
         order = "hclust", 
         tl.col = "black",
         tl.srt = 45)
```

# check 
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
?corrplot
```

# Heatmap 
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
heatmap(correl, symm = TRUE, 
        cexRow = 0.7, 
        cexCol = 0.7)
```

# ggcorrplot
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
p <- ggcorrplot::ggcorrplot(correl, 
                            method = "circle", 
                            type = "lower", 
                            ggtheme = ggplot2::theme_linedraw, 
                            lab_col = "blue", 
                            lab_size = 3,
                            tl.cex = 10, 
                            lab = TRUE, 
                            pch.cex = 10, 
                            colors = c("#6D9EC1", "white", "#E46726")) 
p
p + guides(scale = "none")
```

##----------------------------------------------------------------
##               Fitting Multiple Regression                    --
##----------------------------------------------------------------
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}

model <- lm(replace_mean_Ratings ~ replace_mean_Gross+ replace_mean_Budget+replace_mean_Screens+
            replace_mean_Views+  replace_mean_Likes+replace_mean_Dislikes+replace_mean_Comments+
              replace_mean_Aggregate_Followers, data = movie_data)
model
influencePlot(model)
```

##---------------------------------------------------------------
##                     Checking lm objects                     --
##---------------------------------------------------------------
# Show the components of lm object
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
str(model)
class(model)
typeof(model)
length(model)
names(model)
```

# Summary Function
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
summary(model)
```

# Coefficients Function
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
model$coefficients
```

# Fitted function
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
model$fitted
extract_eq(model,use_cof=TRUE) 
par(mfrow = c(2, 2))
plot(model)
vif(model)
```

## We will improve our result by removing the outlier
##create a boxplot to identify   outliers
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
boxplot(movie_data$replace_mean_Ratings)
boxplot(movie_data$replace_mean_Gross)
boxplot(movie_data$replace_mean_Budget)
boxplot(movie_data$replace_mean_Screens)
boxplot(movie_data$replace_mean_Views)
boxplot(movie_data$replace_mean_Likes)
boxplot(movie_data$replace_mean_Dislikes)
boxplot(movie_data$replace_mean_Comments)
boxplot(movie_data$replace_mean_Aggregate_Followers)
boxplot(movie_data)
boxplot(movie_data)$out
```

###How to Remove Outliers from Multiple Columns in R

```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
cooksd<-cooks.distance((model))

plot(cooksd,pch="*",cex=1,main="Influential obs by cooks distance")

cooksd
```


```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
influential<-cooksd[(cooksd>(3*mean(cooksd,na.rm=TRUE)))]

names_of_influential<-names(influential)
names_of_influential
outliers <- movie_data[names_of_influential,]
movie_data_without_outliers <-movie_data %>% anti_join(outliers)
movie_data_without_outliers

```




#  Other Ways of Removing Outliers ----------------------------------------
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}

outliers <- function(x) {
  
  Q1 <- quantile(x, probs=.25)
  Q3 <- quantile(x, probs=.75)
  iqr = Q3-Q1
  
  upper_limit = Q3 + (iqr*1.5)
  lower_limit = Q1 - (iqr*1.5)
  
  x > upper_limit | x < lower_limit
}

remove_outliers <- function(movie_data, cols = names(movie_data)) {
  for (col in cols) {
    movie_data <- movie_data[!outliers(movie_data[[col]]),]
  }
  movie_data
}

movie_data_without_outliers <- remove_outliers(movie_data)
boxplot(movie_data_without_outliers)
```

```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
mode2 <- lm(replace_mean_Ratings ~  replace_mean_Gross+replace_mean_Budget+
      replace_mean_Screens+replace_mean_Views+replace_mean_Likes+
      replace_mean_Dislikes+replace_mean_Comments+
      replace_mean_Aggregate_Followers, data = movie_data_without_outliers)
mode2
summary(mode2)
```



##mode2

# Coefficients Function &  Fitted function
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
mode2$coefficients
mode2$fitted
extract_eq(mode2,use_cof=TRUE) 
par(mfrow = c(2, 2))
plot(mode2)
```

#### We can see here,that the coefficient is different between our new model and our previous model 
## Also, after removing the outlier from our dataset the residual standard error is decreasing, while the R_ squared is increasing
## It means that our new model fits better to our data compared to the previous model
## VIF for new model

```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
vif(mode2)
glance(mode2)
tidy(mode2)
```



## vif<10 for all variables the model good.


###*************************************************************************
###*************************************************************************
###                                                                      ***
###                          SPLITTING THE DATA                          ***
###                        TRAINING AND TEST SETS                        ***
###                                                                      ***
###*************************************************************************
###*************************************************************************
###*

# Let's say we want to split the data in 80:20 for train :test dataset

```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
set.seed(232)
ind <- createDataPartition(movie_data$ replace_mean_Ratings, 
                           p = 0.8, times = 1, list = FALSE)
length(ind)
train_set <- movie_data[ind, ]
test_set <- movie_data[-ind, ]
nrow(train_set); nrow(test_set)
```


# Training the model ------------------------------------------------------
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
lm_fit <- lm(replace_mean_Ratings ~ . , data = train_set)
broom::tidy(lm_fit)
broom::glance(lm_fit)
```



# We've built a machine learning model and trained it on train_set

###*  *** Prediction ***
#     --------------------
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
pred <- predict(object = lm_fit, newdata = test_set, type = "response") 

head(pred)
```



###       **** Model Evaluation ***
#         -------------------------
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
actual <- test_set$replace_mean_Ratings
mae <- Metrics::mae(actual = actual, predicted = pred)
mse <- Metrics::mse(actual = actual, predicted = pred)
rmse <- Metrics::rmse(actual = actual, predicted = pred)

```


# These common metrics are used to evaluate the model.


# Table of results
```{r}
knitr::kable(cbind(mae, mse, rmse))
```




